Design and Implementation of Probabilistic Programming Language Anglican

### 2016-07-04 paper/paper.tex
formatting issues mostly resolved, now writing

\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{listings}

@@

An Anglican program, or \textit{query}, is compiled into a Clojure
function. When inference is performed with a provided algorithm, this
produces a sequence of return values, or \textit{predicts}. Anglican
shares a common syntax with Clojure; Clojure functions can be called
from Anglican code and vice versa. A simple program in Anglican can
look like the following code:

%\begin{lstlisting}[frame=single,language=Anglican, basicstyle=\ttfamily\small, showstringspaces=false]
%(defquery models
%  "chooses a distribution which describes the data"
%  (let [;; Model -- randomly choose a distribution and parameters
%        dist (sample (categorical [[uniform-discrete 1]
%                                   [uniform-continuous 1]
%                                   [normal 1] 
%                                   [gamma 1]]))
%        a (sample (gamma 1 1)) b (sample (gamma 1 1))
%        d (dist a b)]
%    ;; Data  --- samples from the unknown distribution
%    (observe d 1) (observe d 2) (observe d 4) (observe d 7)
%    ;; Output --- predicted distribution type and parameters
%    (predict :d (type d))
%    (predict :a a) (predict :b b)))
%\end{lstlisting}

>>>>

\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage[lighttt]{lmodern}
\ttfamily
\DeclareFontShape{OT1}{lmtt}{m}{it}
     {<->sub*lmtt/m/sl}{}
	 \usepackage{listings}

@@

An Anglican program, or \textit{query}, is compiled into a Clojure
function. When inference is performed with a provided algorithm, this
produces a sequence of return values, or \textit{predicts}. Anglican
shares a common syntax with Clojure; Clojure functions can be called
from Anglican code and vice versa. A simple program in Anglican can
look like the following code:
\begin{lstlisting}[frame=single,language=Anglican, basicstyle=\ttfamily\small, showstringspaces=false]
(defquery models
  "chooses a distribution
   which describes the data"
  (let [;; Model - randomly choose distribution
	    dist (sample (categorical
                       [[uniform-continuous 1]
                        [normal 1] 
                        [gamma 1]]))
        a (sample (gamma 1 1))
        b (sample (gamma 1 1))
        d (dist a b)]
    ;; Data - samples from the distribution
    (observe d 1)
    (observe d 2)
    (observe d 4)
    (observe d 7)
    ;; Output --- predicted distribution
    (predict :d (type d))
    (predict :a a) (predict :b b)))
\end{lstlisting}
